---
title       : Course Project
subtitle    : Develop Data Products
author      : Mukesh Kanchan
job         : Data Scientist
logo        : logo.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview of Shiny Application

* <span style="color:brown">Application name:</span> 
   
    Dynamic Plot: Normally distributed random numbers 
* <span style="color:brown">Description:</span> 
   
    This application plots normally distributed random data generated by following R fucntion:
```{r eval=FALSE}
rnorm(number, mean, standard_deviation)
```
* <span style="color:brown">Purpose:</span> 
   
    Intension of creating this application is to showcase:     
        - usage of different input widgets     
        - its impact on output     
        - computaion using R code   


--- .class #id 

## Input

1. Number of ramdom samples:     
        - Count parameter to  ```rnorm``` function to generate random numbers
2. Plot type:     
        - Plot type is set to "l", "p", or "o", depending on if line or point or both options are selected
        
3. Set mean:     
        - Mean parameter to  ```rnorm``` function to generate random numbers
4. Set standard deviation:     
        - Standard deviation parameter to  ```rnorm``` function to generate random numbers  
5. Random Data Seed/Change Seed:     
        - Seed value for random number generation
6. Plot color:     
        - Color of plot points and/or line

--- .class #id 

## Output

    
1. Plot - Following code is used to generate the plot (output on next slide - Figure 1)
        
```{r echo=FALSE}
seed <- 1234
num <- 100
mean <- 0
sd <- 1
plotType <- "b"
color <- "blue"
```
```{r echo=TRUE,eval=FALSE}
set.seed(seed)
data <- rnorm(num, mean, sd)
plot(data, type=plotType, col=color, xlab='Number', ylab='Value',
        main=paste('Normal Distribution of Random Data.  [Seed:',paste(seed,']')))
                        
```
2. Summary - FOllowing code is used to provide the summary of randomly generated data     

```{r echo=TRUE,eval=TRUE} 
        summary(data) 
```

--- .class #id 

## Output contd...

Figure 1 : Plot output

```{r echo=FALSE,eval=TRUE}
set.seed(seed)
data <- rnorm(num, mean, sd)
plot(data, type=plotType, col=color, xlab='Number', ylab='Value',
        main=paste('Normal Distribution of Random Data.  [Seed:',paste(seed,']')))
                        
```
```{r echo=FALSE,eval=TRUE} 
        summary(data) 
``` 
---End of Document---
